Reproducible methods for modeling combined public transport and cycling trips and associated benefits: \ evidence from the biclaR tool

### 2024-08-31 paper/PaperCEUS/PaperCEUS_rev2_word.Rmd
setup paper ceus rev2

```{r eval=FALSE, echo=FALSE}
# setwd("paper/PaperCEUS/") # knit directory: Document
system("latexdiff paper/PaperCEUS/PaperCEUS_prerev.tex paper/PaperCEUS/PaperCEUS_rev1.tex > paper/PaperCEUS/PaperCEUS_diff1.tex")
#and change in tex the blue for another color (green? 0,0.5,0) and remove \uwave
# \definecolor{green}{rgb}{0,0.5,0}
# {\protect\color{green}{#1}}}
#and compile PDF!
system("pdflatex paper/PaperCEUS/PaperCEUS_diff1.tex")
```

>>>>

```{r eval=FALSE, echo=FALSE}
# setwd("paper/PaperCEUS/") # knit directory: Document
system("latexdiff paper/PaperCEUS/PaperCEUS_rev1.tex paper/PaperCEUS/PaperCEUS_rev2.tex > paper/PaperCEUS/PaperCEUS_diff2.tex")
#and change in tex the blue for another color (green? 0,0.5,0) and remove \uwave
# \definecolor{green}{rgb}{0,0.5,0}
# {\protect\color{green}{#1}}}
#and compile PDF!
system("pdflatex paper/PaperCEUS/PaperCEUS_diff2.tex")
```
